The paper on \Large \bf Blockchain Frontrunning

### 2018-09-04 frontrunning/Latex/sections/paper.tex
[frontrunning] Intro

\section{Introduction}

Have a small discussion about arbitrage and censorship just to show that they orbit around front-running.
For the FC: \textbf{CASE STUDY} should be used in here, also in abstract, also at the end of intro section.

@@

\subsection{How are Blockchain Applications Vulnerable to Front-running?} %which blockchain applications?
\label{sec:Front Running on the Blockchains}t

>>>>

\section{Introduction}
The history of the \emph{front-running} goes back to the ancient world, where markets in financial instruments were first started. For a trade to take place in those times, all the parties were required to be physically available in the exchange office. Clearly in such scenarios front-running was possible yet not detectable as a damaging activity. However with the rapid advances of the technology in the last few years, trading is not happening in person anymore and a greater amount of applications, whether financial or non-financial, are now vulnerable to front-running. Furthermore, Blockchain technology has introduced a new form of front-running which is inherent in all of the decentral applications. The other two issues which orbit around the front-running, are arbitrage and censorship. However, the goal of this paper is to provide a complete history of the front-running issue and thus the aforemationed will remain out of the scope of this research study. As there has been little quantitative analysis and research of the front-running issue, whether traditional or the new ones on that happen in decentralized application, we aim to take a thorough look into the history of the front-running, systematize all the solutions that have been proposed to this issue so far, and eventually match these solutions to their suitable use cases.\footnote{A note}

%Have a small discussion about arbitrage and censorship just to show that they orbit around front-running.
%For the FC: \textbf{CASE STUDY} should be used in here, also in abstract, also at the end of intro section.

@@

\subsection{How are Blockchain Applications Vulnerable to Front-running?} %which blockchain applications?
\label{sec:Front Running on the Blockchains}
